---
title: "Tag hunt"
author: "Brian Evans"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE) 
```

```{r, include = FALSE}
source("scripts/daily_updates/daily_updates_source.R")
```

<hr>

# Daily overview

```{r, include = FALSE}
detections_by_day <-
  detections %>% 
  mutate(time = as_date(time)) %>% 
  filter(time != today()) %>% 
  group_by(
    time,
    nest_id,
    tag_id)
```


## Pings

The number of daily detections:

```{r, echo = FALSE, fig.asp = 1.5}
detections_by_day %>% 
  summarize(
    n_pings = n(),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_pings,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Nodes

The number of nodes a tag was detected at per day:

```{r, echo = FALSE, fig.asp = 1.5}
detections_by_day %>% 
  summarize(
    n_nodes = 
      length(
        unique(node_id)),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_nodes,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Stdev rssi

The average variance, by node, by day:

```{r, echo = FALSE, fig.asp = 1.5}
detections_by_day %>% 
  summarize(
    sd_rssi = 
      mean(
        sd(rssi),
        na.rm = TRUE),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = sd_rssi,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

<hr>

# The last 2 days, hourly

*Note: To make things easier to interpret, I've subset these records to only observations between sunrise and sunset.*

```{r, include = FALSE}

detections_2_days <- 
  detections %>% 
  filter(time > today() - 2,
         time < today()) %>% 
  mutate(
    date = as_date(time),
    time = round_date(time, "1 hours")) %>% 
  
  # Subset to records between dawn and one hour before dusk:
  
  left_join(
    dawn_dusk,
    by = "date") %>% 
  select(-date) %>%
  filter(
    between(time, dawn, dusk - 3600)) %>% 
  
  # Group data for summaries:
  
  group_by(
    time,
    nest_id,
    tag_id)
```

## Pings

The number of hourly detections over the last two days:

```{r, echo = FALSE, fig.asp = 1.5}
detections_2_days %>% 
  summarize(
    n_pings = n(),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_pings,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Nodes

The number of nodes that a tag was detected at, per hour, over the last two days:

```{r, echo = FALSE, fig.asp = 1.5}
detections_2_days %>% 
  summarize(
    n_nodes = 
      length(
        unique(node_id)),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_nodes,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Stdev rssi

The hourly average standard deviation, by node, over the last two days:

```{r, echo = FALSE, fig.asp = 1.5}
detections_2_days %>% 
  summarize(
    sd_rssi = 
      mean(
        sd(rssi),
        na.rm = TRUE),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = sd_rssi,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

<hr>

# Tag maps

## 34616633

```{r, include = FALSE}
last_observation_34616633 <-
  get_last_observation("34616633", time_window = "2 days") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_34616633 %>% pull(time)` at node `r  last_observation_34616633 %>% pull(node_id)` with an rssi of `r  last_observation_34616633 %>% pull(rssi)`.

```{r}
map_last_time("34616633", time_window = "2 days")
```

<hr>

## 072D782D

```{r, include = FALSE}
last_observation_072D782D <-
  get_last_observation("072D782D", time_window = "2 days") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_072D782D %>% pull(time)` at node `r  last_observation_072D782D %>% pull(node_id)` with an rssi of `r  last_observation_072D782D %>% pull(rssi)`.

```{r}
map_last_time("072D782D", time_window = "2 days")
```

<hr>

## 1E552D19

```{r, include = FALSE}
last_observation_1E552D19 <-
  get_last_observation("1E552D19", time_window = "1 minutes") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_1E552D19 %>% pull(time)` at node `r  last_observation_1E552D19 %>% pull(node_id)` with an rssi of `r  last_observation_1E552D19 %>% pull(rssi)`.

```{r}
map_last_time("1E552D19", time_window = "4 minutes")
```

<hr>

## 55526107

```{r, include = FALSE}
last_observation_55526107 <-
  get_last_observation("55526107", time_window = "1 minutes") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_55526107 %>% pull(time)` at node `r  last_observation_55526107 %>% pull(node_id)` with an rssi of `r  last_observation_55526107 %>% pull(rssi)`.


```{r}
map_last_time("55526107", time_window = "6 hours")
```
