---
title: "Daily update"
author: "Brian Evans"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE) 
```

```{r, include = FALSE}
source("scripts/daily_updates/web_update_source.R")
```

<hr>

# American Kestrel

Here is a summary of yesterday's detections:

```{r, echo = FALSE}
pluck(yesterday_tables, "AMKE")
```

## Daily overview - AMKE 

Stationarity (aka potential death) on the scale of a day can be found by exploring the number of pings (detections), the number of nodes a tag was detected at, and the standard deviation of rssi values. When a tag is stationary, each of these values *should* be quite low.

### Pings - AMKE

The number of daily detections:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(daily_pings, "AMKE")
```

### Nodes - AMKE

The number of nodes a tag was detected at per day:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(daily_nodes, "AMKE")
```

### Stdev rssi - AMKE

The average variance, by node, by day:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(daily_sd, "AMKE")
```

<hr>

## Yesterday, hourly - AMKE

Hourly detections can help find a tag that went stationary *during* a given day and help us pinpoint when a tag went stationary. Look for low detections, number of nodes, and standard deviation values. Focus on situations where multiple adjacent values are low (just one or two may represent resting).

*Note: To make things easier to interpret, I've subset these records to only observations between sunrise and sunset.*

### Pings - AMKE

The number of hourly detections:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(hourly_pings, "AMKE")
```

### Nodes - AMKE

The number of nodes that a tag was detected at, per hour:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(hourly_nodes, "AMKE")
```

### Stdev rssi - AMKE

The hourly average standard deviation, by node:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(hourly_nodes, "AMKE")
```

# Bobolink

Here is a summary of yesterday's detections:

```{r, echo = FALSE}
pluck(yesterday_tables, "BOBO")
```

## Daily overview - BOBO 

Stationarity (aka potential death) on the scale of a day can be found by exploring the number of pings (detections), the number of nodes a tag was detected at, and the standard deviation of rssi values. When a tag is stationary, each of these values *should* be quite low.

### Pings - BOBO

The number of daily detections:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(daily_pings, "BOBO")
```

### Nodes - BOBO

The number of nodes a tag was detected at per day:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(daily_nodes, "BOBO")
```

### Stdev rssi - BOBO

The average variance, by node, by day:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(daily_sd, "BOBO")
```

<hr>

## Yesterday, hourly - BOBO

Hourly detections can help find a tag that went stationary *during* a given day and help us pinpoint when a tag went stationary. Look for low detections, number of nodes, and standard deviation values. Focus on situations where multiple adjacent values are low (just one or two may represent resting).

*Note: To make things easier to interpret, I've subset these records to only observations between sunrise and sunset.*

### Pings - BOBO

The number of hourly detections:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(hourly_pings, "BOBO")
```

### Nodes - BOBO

The number of nodes that a tag was detected at, per hour:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(hourly_nodes, "BOBO")
```

### Stdev rssi - BOBO

The hourly average standard deviation, by node:

```{r, echo = FALSE, fig.asp = 0.5}
pluck(hourly_nodes, "BOBO")
```

# Eastern meadowlark

Here is a summary of yesterday's detections:

```{r, echo = FALSE}
pluck(yesterday_tables, "EAME")
```

## Daily overview - EAME 

Stationarity (aka potential death) on the scale of a day can be found by exploring the number of pings (detections), the number of nodes a tag was detected at, and the standard deviation of rssi values. When a tag is stationary, each of these values *should* be quite low.

### Pings - EAME

The number of daily detections:

```{r, echo = FALSE, fig.asp = 1.5}
pluck(daily_pings, "EAME")
```

### Nodes - EAME

The number of nodes a tag was detected at per day:

```{r, echo = FALSE, fig.asp = 1.5}
pluck(daily_nodes, "EAME")
```

### Stdev rssi - EAME

The average variance, by node, by day:

```{r, echo = FALSE, fig.asp = 1.5}
pluck(daily_sd, "EAME")
```

<hr>

## Yesterday, hourly - EAME

Hourly detections can help find a tag that went stationary *during* a given day and help us pinpoint when a tag went stationary. Look for low detections, number of nodes, and standard deviation values. Focus on situations where multiple adjacent values are low (just one or two may represent resting).

*Note: To make things easier to interpret, I've subset these records to only observations between sunrise and sunset.*

### Pings - EAME

The number of hourly detections:

```{r, echo = FALSE, fig.asp = 1.5}
pluck(hourly_pings, "EAME")
```

### Nodes - EAME

The number of nodes that a tag was detected at, per hour:

```{r, echo = FALSE, fig.asp = 1.5}
pluck(hourly_nodes, "EAME")
```

### Stdev rssi - EAME

The hourly average standard deviation, by node:

```{r, echo = FALSE, fig.asp = 1.5}
pluck(hourly_nodes, "EAME")
```

<hr>

## Tag maps - EAME

### 34616633 - EAME

```{r, include = FALSE}
last_observation_34616633 <-
  get_last_observation("34616633", time_window = "1 days") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_34616633 %>% pull(time)` at node `r  last_observation_34616633 %>% pull(node_id)` with an rssi of `r  last_observation_34616633 %>% pull(rssi)`.

```{r}
map_last_time("34616633", time_window = "2 days")
```

<hr>

### 1E552D19 - EAME

```{r, include = FALSE}
last_observation_1E552D19 <-
  get_last_observation("1E552D19", time_window = "1 minutes") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_1E552D19 %>% pull(time)` at node `r  last_observation_1E552D19 %>% pull(node_id)` with an rssi of `r  last_observation_1E552D19 %>% pull(rssi)`.

```{r}
map_last_time("1E552D19", time_window = "4 minutes")
```

<hr>

### 55526107 - EAME

```{r, include = FALSE}
last_observation_55526107 <-
  get_last_observation("55526107", time_window = "1 minutes") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_55526107 %>% pull(time)` at node `r  last_observation_55526107 %>% pull(node_id)` with an rssi of `r  last_observation_55526107 %>% pull(rssi)`.


```{r}
map_last_time("55526107", time_window = "6 hours")
```

