---
title: "Tag hunt"
author: "Brian Evans"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE) 
```

```{r, include = FALSE}
source("scripts/daily_updates/daily_updates_source.R")
```

<hr>

# Daily overview

Stationarity (aka potential death) on the scale of a day can be found comparing the number of pings (detections), the number of nodes a tag was detected at, and the standard deviation of rssi values. When a tag is stationary, each of these values *should* be quite low.

```{r, include = FALSE}
detections_by_day <-
  detections %>% 
  mutate(time = as_date(time)) %>% 
  filter(time != today()) %>% 
  group_by(
    time,
    nest_id,
    tag_id)
```


## Pings

The number of daily detections:

```{r, echo = FALSE, fig.asp = 1.5}
detections_by_day %>% 
  summarize(
    n_pings = n(),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_pings,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Nodes

The number of nodes a tag was detected at per day:

```{r, echo = FALSE, fig.asp = 1.5}
detections_by_day %>% 
  summarize(
    n_nodes = 
      length(
        unique(node_id)),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_nodes,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Stdev rssi

The average variance, by node, by day:

```{r, echo = FALSE, fig.asp = 1.5}
detections_by_day %>% 
  summarize(
    sd_rssi = 
      mean(
        sd(rssi),
        na.rm = TRUE),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = sd_rssi,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

<hr>

# The last 2 days, hourly

Hourly detetinos can help find a tag that went stationary *during* a given day and help us pinpoint when.a tag went stationary. As above, look for low detections, number of nodes, and standard deviation values. Focus on situations where multiple adjacent values are low (just one or two may represent resting).

*Note: To make things easier to interpret, I've subset these records to only observations between sunrise and sunset.*

```{r, include = FALSE}

detections_2_days <- 
  detections %>% 
  filter(time > today() - 2,
         time < today()) %>% 
  mutate(
    date = as_date(time),
    time = round_date(time, "1 hours")) %>% 
  
  # Subset to records between dawn and one hour before dusk:
  
  left_join(
    dawn_dusk,
    by = "date") %>% 
  select(-date) %>%
  filter(
    between(time, dawn, dusk - 3600)) %>% 
  
  # Group data for summaries:
  
  group_by(
    time,
    nest_id,
    tag_id)
```

## Pings

The number of hourly detections over the last two days:

```{r, echo = FALSE, fig.asp = 1.5}
detections_2_days %>% 
  summarize(
    n_pings = n(),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_pings,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Nodes

The number of nodes that a tag was detected at, per hour, over the last two days:

```{r, echo = FALSE, fig.asp = 1.5}
detections_2_days %>% 
  summarize(
    n_nodes = 
      length(
        unique(node_id)),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = n_nodes,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

## Stdev rssi

The hourly average standard deviation, by node, over the last two days:

```{r, echo = FALSE, fig.asp = 1.5}
detections_2_days %>% 
  summarize(
    sd_rssi = 
      mean(
        sd(rssi),
        na.rm = TRUE),
    .groups = "drop") %>% 
  ggplot() +
  aes(x = time,
      y = sd_rssi,
      color = tag_id) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~ nest_id, 
    scales = "free",
    ncol = 1) +
  daily_update_theme()
```

<hr>

# Tag maps

## 34616633

```{r, include = FALSE}
last_observation_34616633 <-
  get_last_observation("34616633", time_window = "1 days") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_34616633 %>% pull(time)` at node `r  last_observation_34616633 %>% pull(node_id)` with an rssi of `r  last_observation_34616633 %>% pull(rssi)`.

```{r}
map_last_time("34616633", time_window = "2 days")
```

<hr>

## 1E552D19

```{r, include = FALSE}
last_observation_1E552D19 <-
  get_last_observation("1E552D19", time_window = "1 minutes") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_1E552D19 %>% pull(time)` at node `r  last_observation_1E552D19 %>% pull(node_id)` with an rssi of `r  last_observation_1E552D19 %>% pull(rssi)`.

```{r}
map_last_time("1E552D19", time_window = "4 minutes")
```

<hr>

## 55526107

```{r, include = FALSE}
last_observation_55526107 <-
  get_last_observation("55526107", time_window = "1 minutes") %>%
  slice_max(time, n = 1)
```

The tag was last seen on `r  last_observation_55526107 %>% pull(time)` at node `r  last_observation_55526107 %>% pull(node_id)` with an rssi of `r  last_observation_55526107 %>% pull(rssi)`.


```{r}
map_last_time("55526107", time_window = "6 hours")
```
